---
title: "Reproducible Research: Peer Assessment 1"
output: 
  html_document:
    keep_md: true
---


## Loading and preprocessing the data
Load libraries to be used in analysis
```{r loadLibraries, message=FALSE}
library(dplyr)
library(ggplot2)
```


Read in the data and view a summary
```{r loadData}
allData <- read.csv("activity.csv")
summary(allData)
```

Group data by day
```{r dayData}
dayData <- allData %>% group_by(date) %>% summarize(sumSteps = sum(steps))
```

## What is mean total number of steps taken per day?

Histogram for the total number of steps taken per day
```{r totalSteps}
hist(dayData$sumSteps, breaks = 10, col = "blue", main = "Total Number of Steps 
     per Day", xlab = "Steps")
```

Calculate the mean and median total number of steps taken per day
```{r meanMedSteps}
meanSteps <- mean(dayData$sumSteps, na.rm = TRUE)
medianSteps <- median(dayData$sumSteps, na.rm = TRUE)
```

Mean steps per day: `r format(meanSteps, scientific = FALSE, big.mark=",")`  
Median steps per day: `r format(medianSteps, big.mark=",")`

## What is the average daily activity pattern?



## Imputing missing values



## Are there differences in activity patterns between weekdays and weekends?
